Canonical rings of log spin stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
some rewording to new remarks from aaron

\begin{rem}
\label{rem:genus-1-explicit-bound}
In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, the proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations. That, is one can start with the generators and relations found in the base cases and inductively add in generators and relations as one adds and then increments stacky points. As described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e: = \max(e_1,\ldots, e_r) \geq 7$, there is necessarily a generator in degree $e$ and a relation in degree $2e$.
\end{rem}

@@

\begin{rem}
\label{rem:genus-0-explicit-bound}
Similarly to the case of genus 1, as described in Remark ~\ref{rem:genus-1-explicit-bound}, the proof of Theorem ~\ref{thm:g-0-main} gives an explicit construction of the generators and relations for the log spin canonical ring $R_L$. Furthermore, as described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e := \max(e_1, \ldots, e_r)$ is at least $7$, there is a generator in degree $e$ and a relation in degree at least $2e-4$. This can be seen from the inductive application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref{lem:sat-3}.
\end{rem}

\begin{rem}
\label{rem:cusp-generation-4}
Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}. A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in weight at most 4. Since $\delta > 0$, $L_X$ is effective. Addtionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8. Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8. Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in weight at most 4 with relations in weight at most 8.
\end{rem}

>>>>

\begin{rem}
\label{rem:genus-1-explicit-bound}
In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, the proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations. One can start with the generators and relations found in the base cases and inductively add generators and relations as one adds stacky points and increments stabilizer orders. As described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e := \max(e_1,\ldots, e_r) \geq 7$, there is necessarily a generator in degree $e$ and a relation in degree $2e$.
\end{rem}

@@

\begin{rem}
\label{rem:genus-0-explicit-bound}
The proof of Theorem ~\ref{thm:g-0-main} in genus zero gives an
explicit construction of the generators and relations for the log
spin canonical ring $R_L$. This is similar to the case of genus 1
in Remark ~\ref{rem:genus-1-explicit-bound}. Furthermore, there is
a generator in degree $e$ and a relation in degree at least $2e-4$
when $e := \max(e_1, \ldots, e_r)$ is at least $7$ (see Remark ~\ref
{rem:genus-2-explicit-bound}). This can be seen from the inductive
application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref
{lem:sat-3}.
\end{rem}

\begin{rem}
\label{rem:cusp-generation-4}
Here, we describe how to obtain a slightly better bound for our
application to modular forms from example ~\ref{eg:congruence-bounds}.
A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that,
if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$
, then $R_L$ is generated in weight at most 4. Since $\delta > 0$,
$L_X$ is effective. Additionally, $R_{L_X}$ is generated in weight 1
, and inductive applications of Lemma ~\ref{lem:sat-1} only add
generators in weights 3 and 4 and relations in weight at most 8.
Therefore, $R_L$ is generated in weight at most 4 with relations in
weight at most 8. Note that a similar analysis of the proof of
Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence
subgroups are generated in weight at most 4 with relations in
weight at most 8.
\end{rem}

%%%%%%%%%%%%%%%%%%%%%%%%% Further Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%
